Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
Method chaining.

\textbf{Predictors.} The \textit{predictor} interface defines a \texttt{predict}
method taking as input some new data \texttt{X\_test} and producing as output
predictions for \texttt{X\_test} based on the learned parameters of the
estimator. In the case of supervised learning estimators, this method typically
returns the predicted labels or values computed by the model.  Continuing with
the previous example, predicted labels for \texttt{X\_test} can be obtained
using the following snippet:
\begin{verbatim}
y_pred = clf.predict(X_test)
\end{verbatim}
Some unsupervised learning
estimators may however also implement that interface, as illustrated below:
\begin{verbatim}
from sklearn.cluster import KMeans
km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{verbatim}
In the above example, a \texttt{KMeans} estimator is first fit on the training
data \texttt{X\_train}. Then the \texttt{predict} method is called on the test
data \texttt{X\_test} in order to retrieve predicted cluster labels.
The \texttt{predict} method in \textit{scikit-learn} thus offers a unified way
to compute predictions with respect to unseen data.

Along with the \texttt{predict} method, predictors may also implement methods
for quantifying the certainty of a prediction. In the case of estimators
implementing linear models, the \texttt{decision\_function} method can be used
to measure the distance of the samples from the discriminating hyperplane. Some
predictors also provide a \texttt{predict\_proba} method which returns
class probabilities for the input samples \texttt{X}.

Finally, predictors should also provide a \texttt{score} function to assess the
goodness of fit on some input data. In supervised learning estimators, this
method takes as inputs a dataset \texttt{X} and \texttt{y} and typically
computes the coefficient of determination between \texttt{y} and
\texttt{predict(X)} in the case of classification or the mean squared error in
the case of regression. Not however that, from an API point of view, the only
guideline is that the \texttt{score} method returns a numerical value such that
the higher the better. As such, some unsupervised learning estimators also
exposes a \texttt{score} function, computing for instance the likelihood of the
given data.

\textbf{Transformers.} Since it is common to modify or filter data before
feeding it to a learning algorithm, some estimators in the library implement a
\textit{transformer} interface which defines a \texttt{transform} method. It
takes as input some dataset \texttt{X} and yields as output a transformed
version of \texttt{X}\footnote{From an implementation point of view, it may
sometimes be more efficient to implement \texttt{fit} and \texttt{transform} in
a single method. In that case, transformers may expose an additional
\texttt{fit\_transform} method.}. In particular, all preprocessing algorithms
and feature selection routines are offered as transformers within the library.

In our example, if one wanted to transform the inputs \texttt{X\_train} before
fitting the logistic regression estimator, e.g., by standardizing the feature values,
one could thus simply write:
\begin{verbatim}
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{verbatim}

Note that the snippet relies on the fact that the \texttt{fit} method always
returns the object it was called on , hence making method chaining  possible.

@@

\subsection{Composition}

>>>>

\textbf{Predictors.} The \textit{predictor} interface defines a \texttt{predict}
method taking as input some new data \texttt{X\_test} and producing as output
predictions for \texttt{X\_test}, based on the learned parameters of the
estimator (we call the input to \texttt{predict} ``\texttt{X\_test}'' in order
to emphasize that \texttt{predict} generalizes to new data; however,
\texttt{predict} can also be called on \texttt{X\_train}). In the case of
supervised learning estimators, this method typically returns the predicted
labels or values computed by the model.  Continuing with the previous example,
predicted labels for \texttt{X\_test} can be obtained using the following
snippet:
\begin{verbatim}
y_pred = clf.predict(X_test)
\end{verbatim}
Some unsupervised learning
estimators may however also implement that interface, as illustrated below:
\begin{verbatim}
from sklearn.cluster import KMeans
km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{verbatim}
In the above example, a \texttt{KMeans} estimator is first fit on the training
data \texttt{X\_train}. Then the \texttt{predict} method is called on the test
data \texttt{X\_test} in order to retrieve predicted cluster labels.
The \texttt{predict} method in \textit{scikit-learn} thus offers a unified way
to compute predictions with respect to unseen data.

Along with the \texttt{predict} method, predictors may also implement methods
for quantifying the certainty of a prediction. In the case of estimators
implementing linear models, the \texttt{decision\_function} method can be used
to measure the distance of the samples from the discriminating hyperplane. Some
predictors also provide a \texttt{predict\_proba} method which returns
class probabilities for the input samples \texttt{X\_test}.

Finally, predictors should also provide a \texttt{score} function to assess the
performance on some input data. In supervised learning estimators, this method
takes as inputs a dataset \texttt{X\_test} and \texttt{y\_test} and typically
computes the coefficient of determination between \texttt{y\_test} and
\texttt{predict(X\_test)} in the case of classification or the mean squared
error in the case of regression. Not however that, from an API point of view,
the only guideline is that the \texttt{score} method returns a numerical value
such that the higher the better. As such, some unsupervised learning estimators
also exposes a \texttt{score} function, computing for instance the likelihood of
the given data.

\textbf{Transformers.} Since it is common to modify or filter data before
feeding it to a learning algorithm, some estimators in the library implement a
\textit{transformer} interface which defines a \texttt{transform} method. It
takes as input some new data \texttt{X\_test} and yields as output a transformed
version of \texttt{X\_test} Preprocessing, feature selection and dimensionality
reduction algorithms are all provided as transformers within the library.  In
our example, if one wanted to preprocess the inputs \texttt{X\_train} before
fitting the logistic regression estimator, e.g., by standardizing the feature
values, one could thus simply write:
\begin{verbatim}
scaler = StandardScaler()
scaler.fit(X_train)
X_train = scaler.transform(X_train)
\end{verbatim}
Of course, in practice, it is important to apply the same preprocessing to the
test data \texttt{X\_test}. This can easily be done as follows:
\begin{verbatim}
X_test = scaler.transform(X_test)
\end{verbatim}

\subsection{Method chaining}

In \textit{scikit-learn}, the \texttt{fit} method always returns the estimator
it was called on, hence making method chaining possible.  Using this technique,
we can thus rewrite the \texttt{StandardScaler} example above in a single line:
\begin{verbatim} 
X_train = StandardScaler().fit(X_train).transform(X_train)
\end{verbatim} 
In \textit{scikit-learn}, \texttt{fit(X\_train).transform(X\_train)} can further
be rewritten as \texttt{fit\_transform(X\_train)}.  Combining the \texttt{fit}
and \texttt{transform} methods into a single method \texttt{fit\_transform}
allows to share computations, which often makes a huge difference in practice.
In the same spirit, \textit{scikit-learn} sometimes provides the
\texttt{fit\_predict} method for combining the \texttt{fit} and \texttt{predict}
methods. This is especially useful for retrieving cluster predictions with
respect to the training data \texttt{X\_train} in clustering algorithms.

@@

\subsection{Estimator composition}
